Enhancement of SDR in Thessaloniki

### 2024-04-11 high_aod/GHI_enh_02_ID_CE.tex
Commit 2024-04-11 03:12

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-09}

@@

@@

\begin{verbatim}
 [1] "Exact_B.High_W.edir"  "Exact_B.High_W.edn"   "Exact_B.High_W.eup"  
 [4] "Exact_B.Low_2_W.edir" "Exact_B.Low_2_W.edn"  "Exact_B.Low_2_W.eup" 
 [7] "Exact_B.Exact_W.edir" "Exact_B.Exact_W.edn"  "Exact_B.Exact_W.eup" 
[10] "Exact_B.Low_W.edir"   "Exact_B.Low_W.edn"    "Exact_B.Low_W.eup"   
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{switch}\NormalTok{(csmodel,}
       \AttributeTok{Exact\_B.Exact\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.02}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{55}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_2\_B.Low\_2\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.03}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{5}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Exact\_W   =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.04}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.High\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
\NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
\DocumentationTok{\#\# init flag}
\NormalTok{DATA[, Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}

@@

\begin{verbatim}
 [1]        NA        NA 0.9855379 0.9053113 0.8366196 0.7771548 0.7251860 0.6793893
 [9] 0.6387354 0.6024114 0.5697672
\end{verbatim}

@@

\begin{verbatim}
C4 factor: 1.05 
\end{verbatim}

@@

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_4}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
5785494 & 416673 \\
\end{longtable}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-223} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-224} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-225} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-226} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-227} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-228} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-229} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-230} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-231} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-232} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-233} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-234} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-235} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-236} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-237} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-238} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-239} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-240} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-241} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-242} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-243} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-244} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-245} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-246} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-247} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-248} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-249} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-250} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-251} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-252} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-253} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-254} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-255} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-256} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-257} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-258} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-259} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-260} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-261} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-262} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-263} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-264} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-265} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_days-266} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_02_ID_CE_files/figure-latex/example_years-31} \end{center}

@@

\begin{verbatim}
2024-04-09 19:11:13.0 athan@tyler GHI_enh_02_ID_CE.R 62.482203 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-10}

@@

\begin{verbatim}
Warning:

 ** Test is active!! ** 
\end{verbatim}

@@

\begin{verbatim}
 [1] "Exact_B.High_W.edir"  "Exact_B.High_W.edn"   "Exact_B.High_W.eup"   "Exact_B.Low_2_W.edir"
 [5] "Exact_B.Low_2_W.edn"  "Exact_B.Low_2_W.eup"  "Exact_B.Exact_W.edir" "Exact_B.Exact_W.edn" 
 [9] "Exact_B.Exact_W.eup"  "Exact_B.Low_W.edir"   "Exact_B.Low_W.edn"    "Exact_B.Low_W.eup"   
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{switch}\NormalTok{(csmodel,}
       \AttributeTok{Exact\_B.Exact\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.02}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{55}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_2\_B.Low\_2\_W =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.03}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{5}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Exact\_W   =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.04}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.High\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}} \DecValTok{20}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.12}\NormalTok{\},}
       \AttributeTok{Low\_B.Low\_W     =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.05}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.18}\NormalTok{\},}
       \AttributeTok{High\_B.Low\_W    =}\NormalTok{ \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.10}\NormalTok{; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}} \DecValTok{60}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \FloatTok{1.25}\NormalTok{\}, }\DocumentationTok{\#\# same as the used criterio}
\NormalTok{                         \{ C4\_cs\_ref\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   ; C4\_GLB\_diff\_THRES }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_sza }\OtherTok{\textless{}{-}}  \DecValTok{0}\NormalTok{; C4\_lowcut\_ratio }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{   \})}
\DocumentationTok{\#\# init flag}
\NormalTok{DATA[, Enhanc\_C\_4 }\SpecialCharTok{:=} \ConstantTok{FALSE}\NormalTok{]}

@@

\begin{verbatim}
 [1]        NA        NA 1.0440020 0.9584892 0.8852695 0.8218832 0.7664852 0.7176648 0.6743248
[10] 0.6355989 0.6007941
\end{verbatim}

@@

\begin{verbatim}
C4 factor: 1.1 
\end{verbatim}

@@

\begin{longtable}[]{@{}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1389}}@{}}
\caption{Enhanc\_C\_4}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedleft
FALSE
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
TRUE
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
6031301 & 170866 \\
\end{longtable}

@@

@@

\begin{verbatim}
Warning: TEST IS ACTIVE !!
\end{verbatim}

TEST IS ACTIVE !!

@@

\begin{verbatim}
2024-04-10 14:41:06.4 athan@tyler GHI_enh_02_ID_CE.R 8.094902 mins
\end{verbatim}

### 2024-04-11 high_aod/GHI_enh_03_process.tex
Commit 2024-04-11 03:12

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-08}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}

 USING CSMODE: Low_B.Low_W

C4 factor: 1.05 
C4 offset: 0 
\end{verbatim}

@@

\begin{verbatim}
2024-04-08 15:48:57.0 athan@sagan GHI_enh_02_ID_CE.R 29.123272 mins
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-372.77 -150.51  -49.67   99.05  778.55

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -9.118e+01  5.082e+01  -1.794   0.0736 .  
as.numeric(Date)  3.246e-07  4.062e-08   7.991 1.82e-14 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 217 on 361 degrees of freedom
Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-372.77 -150.51  -49.67   99.05  778.55

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -9.118e+01  5.082e+01  -1.794   0.0736 .  
ST_E_monthly$Date  3.246e-07  4.062e-08   7.991 1.82e-14 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 217 on 361 degrees of freedom
Multiple R-squared:  0.1503,    Adjusted R-squared:  0.148 
F-statistic: 63.86 on 1 and 361 DF,  p-value: 1.815e-14
\end{verbatim}

@@

\begin{verbatim}
2024-04-08 15:55:25.5 athan@sagan GHI_enh_02_ID_CE.R 3.671820 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-10}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Warning in eval(ei, envir):

 ** Test is active!! ** 
\end{verbatim}

 USING CSMODE: High_B.Low_W

C4 factor: 1.1 
C4 offset: 0 
\end{verbatim}

@@

\begin{verbatim}
Warning in eval(ei, envir): TEST IS ACTIVE !!
\end{verbatim}

  TEST IS ACTIVE  !!

2024-04-10 14:55:07 athan@tyler GHI_enh_02_ID_CE.R 6.972880 mins
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-922.49 -337.13  -68.82  261.22 1657.04

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -1.886e+02  1.075e+02  -1.754   0.0802 .  
as.numeric(Date)  7.871e-07  8.610e-08   9.141   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 463.1 on 364 degrees of freedom
Multiple R-squared:  0.1867,    Adjusted R-squared:  0.1845 
F-statistic: 83.56 on 1 and 364 DF,  p-value: < 2.2e-16
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-922.49 -337.13  -68.82  261.22 1657.04

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -1.886e+02  1.075e+02  -1.754   0.0802 .  
ST_E_monthly$Date  7.871e-07  8.610e-08   9.141   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 463.1 on 364 degrees of freedom
Multiple R-squared:  0.1867,    Adjusted R-squared:  0.1845 
F-statistic: 83.56 on 1 and 364 DF,  p-value: < 2.2e-16
\end{verbatim}

@@

\begin{verbatim}
2024-04-10 15:18:08 athan@tyler GHI_enh_02_ID_CE.R 17.930279 mins
\end{verbatim}
